### 2022-10-08 R0-Density-Reanalysis/_R0-Density-Reanalysis.Rmd
Updated with final bibliographical information and created a renv reproducible environment

---
title: "Reproducibility of research during COVID-19: examining the case of population density and the basic reproductive rate from the perspective of spatial analysis"
author:
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    correspondingauthor: true
address:
  - code: McMaster University
    address: School of Earth, Environment and Society, 1280 Main St West, Hamilton, Ontario L8S 4K1 Canada
abstract: |
  The emergence of the novel SARS-CoV-2 coronavirus and the global COVID-19 pandemic in 2019 led to explosive growth in scientific research. Alas, much of the research in the literature lacks conditions to be reproducible, and recent publications on the association between population density and the basic reproductive number of SARS-CoV-2 are no exception. Relatively few papers share code and data sufficiently, which hinders not only verification but additional experimentation. In this paper, an example of reproducible research shows the potential of spatial analysis for epidemiology research during COVID-19. Transparency and openness means that independent researchers can, with only modest efforts, verify findings and use different approaches as appropriate. Given the high stakes of the situation, it is essential that scientific findings, on which good policy depends, are as robust as possible; as the empirical example shows, reproducibility is one of the keys to ensure this.

  This paper is now published in Geographical Analysis (\url{https://doi.org/10.1111/gean.12307})
keywords: 
  - keyword1
  - keyword2
journal: "Geographical Analysis"
date: "Final form published in Volume 54, Issue 4"
classoption: preprint, 3p, authoryear
bibliography: bibliography.bib
linenumbers: true
numbersections: false
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
---

@@

```{r load-packages, include=FALSE, cache=FALSE}
library(adespatial) # Used to calculate Moran eigenvector maps
library(censReg) # Package to estimate tobit model
library(here) # A Simpler Way to Find Your Files
library(kableExtra) # Package for creating tables
library(Matrix) # Used to convert list of spatial weights to sparse matrix; needed for spatialprobit
library(nlme) # Used to estimate 
library(patchwork) # Package to organize ggplot2 plots
library(rticles) # Article Formats for R Markdown
library(sampleSelection) # Package to estimate sampling selection models
library(scico) # Package with color palettes
library(sf) # Package to work with spatial information in simple features format
library(spatialprobit) # Used to estimate spatially autoregressive tobit
library(spdep) # Utilities to create spatial weights and work with spatial data
library(tidycensus) # Package to retrieve census information 
library(tidyverse) # Data carpentry and analysis tools
library(units) # Package to work with units of measurement
```

>>>>

---
title: "Reproducibility of research during COVID-19: examining the case of population density and the basic reproductive rate from the perspective of spatial analysis"
author:
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
address:
  - code: McMaster University
    address: School of Earth, Environment and Society, 1280 Main St West, Hamilton, Ontario L8S 4K1 Canada
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  The emergence of the novel SARS-CoV-2 coronavirus and the global COVID-19 pandemic in 2019 led to explosive growth in scientific research. Alas, much of the research in the literature lacks conditions to be reproducible, and recent publications on the association between population density and the basic reproductive number of SARS-CoV-2 are no exception. Relatively few papers share code and data sufficiently, which hinders not only verification but additional experimentation. In this paper, an example of reproducible research shows the potential of spatial analysis for epidemiology research during COVID-19. Transparency and openness means that independent researchers can, with only modest efforts, verify findings and use different approaches as appropriate. Given the high stakes of the situation, it is essential that scientific findings, on which good policy depends, are as robust as possible; as the empirical example shows, reproducibility is one of the keys to ensure this.

  This paper is now published in Geographical Analysis (\url{https://doi.org/10.1111/gean.12307})

journal: "Geographical Analysis"
date: "`r Sys.Date()`"
bibliography: bibliography.bib
linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
header-includes:
    - \usepackage{setspace}\onehalfspacing    
---

@@

```{r load-packages, include=FALSE, cache=FALSE}
library(adespatial) # Used to calculate Moran eigenvector maps
library(censReg) # Package to estimate tobit model
library(here) # A Simpler Way to Find Your Files
library(kableExtra) # Package for creating tables
library(Matrix) # Used to convert list of spatial weights to sparse matrix; needed for spatialprobit
library(nlme) # Used to estimate 
library(patchwork) # Package to organize ggplot2 plots
library(sampleSelection) # Package to estimate sampling selection models
library(scico) # Package with color palettes
library(sf) # Package to work with spatial information in simple features format
library(spatialprobit) # Used to estimate spatially autoregressive tobit
library(spdep) # Utilities to create spatial weights and work with spatial data
library(tidycensus) # Package to retrieve census information 
library(tidyverse) # Data carpentry and analysis tools
library(units) # Package to work with units of measurement
```

### 2022-10-08 README.Rmd
Updated with final bibliographical information and created a renv reproducible environment

Geographical Analysis (2021) https://doi.org/10.1111/gean.12307

@@

```{r install-data-package, include=FALSE}
if(!require(r0density)){
    remotes::install_github("paezha/Reproductive-Rate-and-Density-US-Reanalyzed", 
                         subdir = "r0density")
    library(r0density)
}
```

```{r load-packages, include=FALSE, cache=FALSE}
library(adespatial) # Used to calculate Moran eigenvector maps
library(censReg) # Package to estimate tobit model
library(kableExtra) # Package for creating tables
library(Matrix) # Used to convert list of spatial weights to sparse matrix; needed for spatialprobit
library(nlme) # Used to estimate 
library(patchwork) # Package to organize ggplot2 plots
library(r0density) # Data package
library(sampleSelection) # Package to estimate sampling selection models
library(scico) # Package with color palettes
library(sf) # Package to work with spatial information in simple features format
library(spatialprobit) # Used to estimate spatially autoregressive tobit
library(spdep) # Utilities to create spatial weights and work with spatial data
library(tidycensus) # Package to retrieve census information 
library(tidyverse) # Data carpentry and analysis tools
library(units) # Package to work with units of measurement
#library(viridis) # Color palettes
```

>>>>

Paez, A (2022) Reproducibility of Research During COVID-19: Examining the Case of Population Density and the Basic Reproductive Rate from the Perspective of Spatial Analysis. Geographical Analysis. 54(4) 860-880 (https://doi.org/10.1111/gean.12307)

@@

```{r load-packages, include=FALSE, cache=FALSE}
library(adespatial) # Used to calculate Moran eigenvector maps
library(censReg) # Package to estimate tobit model
library(here) # A Simpler Way to Find Your Files
library(kableExtra) # Package for creating tables
library(Matrix) # Used to convert list of spatial weights to sparse matrix; needed for spatialprobit
library(nlme) # Used to estimate 
library(patchwork) # Package to organize ggplot2 plots
library(sampleSelection) # Package to estimate sampling selection models
library(scico) # Package with color palettes
library(sf) # Package to work with spatial information in simple features format
library(spatialprobit) # Used to estimate spatially autoregressive tobit
library(spdep) # Utilities to create spatial weights and work with spatial data
library(tidycensus) # Package to retrieve census information 
library(tidyverse) # Data carpentry and analysis tools
library(units) # Package to work with units of measurement
```

```{r install-data-package, include=FALSE}
if(!require(r0density)){
    install.packages(paste0(here(), "/r0density_0.1.0.tar.gz"), repos = NULL, type="source")
    library(r0density) # not installed on this machine
}
```

```{r load-data-package, include=FALSE, cache=FALSE}
library(r0density) # Data package
```
